---
title: "Prediction Assignment"
author: "Zhao"
date: "September 23, 2018"
output: html_document
---
## Executive Summary
The goal of this project is to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants to predict the manner in which they did the exercise. This is the "classe" variable in the training set. 

A validation set is sub-setted from the original training set to validate the modle built based on the training subset, with a random forest model using 54 of the predictors in the training sub-set. accuracy is above 99% for both the training sub-set and validation sub-set.

I also use your prediction model to predict 20 different test cases in the test set, with a 100% accuracy.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,cache = TRUE)
```

### 1. Load libraries needed,create a d folder and download the data into the folder. Enable prrallel running to speedup the modeling
```{r}
library(parallel)
library(doParallel)
registerDoParallel(makeCluster(detectCores()- 1))


library(caret)
library(randomForest)

trainURL <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
download.file(trainURL,destfile = "./pml-training.csv")

testURL <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"
download.file(testURL,destfile = "./pml-testing.csv")
```

### 2. Load the training and testing data set, select the preedictors by removing columns with NA as majority, then sub-set the training set
```{r}
trainset <- read.csv("pml-training.csv",na.strings = c("",NA))
trainset <- trainset[,colSums(is.na(trainset))<19000][,-(1:5)]
inTrain = createDataPartition(trainset$classe, p = 0.6,list=FALSE)
training = trainset[inTrain,]
validation = trainset[-inTrain,]
testing <- read.csv("pml-testing.csv")
```

### 3. Build the random forest model based on the training set and check the accuracy
```{r}
modrf <- train(classe~.,method="rf",data=training,trControl=trainControl(method = "cv",number = 2,allowParallel = TRUE))
confusionMatrix(modrf)
```

### 4. Validate the modle with the validation set and confirm the accuracy
```{r}
validate <- predict(modrf,validation)
confusionMatrix(validate,validation$classe)
```

### 5. Predict 20 different test cases in the test set
```{r}
predTestrf <- predict(modrf,testing)
print(predTestrf)
```

### 6. Stop the parallel running
```{r}
stopCluster(makeCluster(detectCores()- 1))
registerDoSEQ()
```


